Article 1 : Pathway found for treatment-resistant lung cancer

### 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
ajout du lien vers le pdf
date article + nbre de mots

Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.

>>>>

Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>, published on 23 September 2019

Article with highlighted words : https://github.com/aureliepinchart/aurelie-pinchart-blog/blob/master/pdf/article_1.pdf

Word count : 1055
